Geometrization of characters of tori over non-Archimedean local fields

### 2013-08-14 shanghai.tex
Reasons for geometrization in the introduction

>>>>

We have not yet fully explored the applications of such a geometrization, but want to highlight
some of the potential benefits of Theorem \ref{thm:application}.  Characters on $T$ have limited
functoriality: they can be pulled back along maps to $T$, but it is less clear what to do with them
in the presence of maps from $T$ to other reductive groups.  Sheaves, on the other hand, come
equipped with a host of functors, including pushforward.

In recent years various authors have applied Deligne-Lusztig representations to the
local Langlands correspondence \cite{}.  The next step Lusztig took in studying representations
of finite groups of Lie type was to define character sheaves for reductive groups over $\Fq$.
We hope that our quasicharacter sheaves can provide a stepping stone to a similar theory for
representations of $p$-adic groups.

The scope of the Langlands program has grown explosively in the past several decades, and
different parts of it apply to different kinds of representations.  In particular, the classic local Langlands
correspondence addresses complex (or $\ell$-adic) representations of real and $p$-adic groups, while
the geometric Langlands program aims at representations of groups in characteristic $p$.  The fact that
characteristic $p$ group schemes arise as the space underlying quasicharacter sheaves, regardless of
the characteristic of $K$, provides a potential bridge allowing the methods of the geometric Langlands
program to be applied to the classic context.

Finally, we are tantalized by the possibility of providing an alternate perspective on local class field theory
through quasicharacter sheaves.  The local Langlands correspondence for tori provides an isomorphism
\[
\Hh^1(\Weil{K}, \hat{T}) \cong \Hom(T(K), \EEx).
\]
A geometric description of the resulting isomorphism $\Hh^1(\Weil{K}, \hat{T}) \cong \QCiso{\GN{T}}$
would yield a different description of the Artin reciprocity map.
